### 2021-06-22 src/paper/report.tex
Update group specific share known cases number.

Modelling a population of agents according to actual demographic characteristics means
that we can use a wide array of data to identify and estimate the model's many
parameters.\footnote{See section~\ref{sec:data_and_parameters} of the supplementary
materials for an overview.} Contact diaries yield pre-pandemic distributions of contacts
for different contact types and their assortativity by age group. Mobility data is used
to model the evolution of work contacts. School and daycare policies can be incorporated
directly from official directives. Administrative records on the number of tests,
vaccinations by age and region, and the prevalence of virus strains are generally
available. Surveys may ask about test offers, propensities to take them up, and past
tests. Other studies' estimates of the seasonality of infections can be incorporated
directly. The remaining parameters---most notably, these include infection probabilities
by contact network and the effects of NPIs, see Supplementary
Material~\ref{subsec:estimated_params}---will be chosen numerically so that the model
matches features of the data \citep[see][for the general method, also described in
Supplementary Material \ref{sec:model}]{McFadden1989}.\comment[id=HM]{Make referencemore
specific once Appendix has new structure} In our application, we keep the number of free
parameters low in order to avoid overfitting. The data features to be matched include
official case numbers for each age group and region, deaths, and the share of the B.1.1.7
strain.

The main issue with official case numbers is that they will contain only a fraction of
all infections. We thus model official cases as depicted in
Figure~\ref{fig:model_official_cases}.\comment[id=K]{I don't understand why we mention
the false positive rates in the floatfoot of this. I would either mention rapid test
sensitivity and specificity in general or not mention them at all.} We take aggregate
estimates of the share of detected cases and use data on whether CoViD-19 symptoms led to
a PCR test. As the share of asymptomatic individuals varies by age group, this gives us
age-specific shares (see Figure~\ref{fig:share_known_cases_by_age_group} for the share of
known cases by age group over time in our model). Our estimates suggest that---in the
absence of rapid testing---the detection rate is two to three times higher for
individuals above age 80 compared to school age children.\comment[id=K]{Must be verified
once results are final.} Once rapid test become available, confirmation of a positive
result is another reason leading to positive PCR tests.

>>>>

Modelling a population of agents according to actual demographic characteristics means
that we can use a wide array of data to identify and estimate the model's many
parameters.\footnote{See section~\ref{sec:data_and_parameters} of the supplementary
materials for an overview.} Contact diaries yield pre-pandemic distributions of contacts
for different contact types and their assortativity by age group. Mobility data is used
to model the evolution of work contacts. School and daycare policies can be incorporated
directly from official directives. Administrative records on the number of tests,
vaccinations by age and region, and the prevalence of virus strains are generally
available. Surveys may ask about test offers, propensities to take them up, and past
tests. Other studies' estimates of the seasonality of infections can be incorporated
directly. The remaining parameters---most notably, these include infection probabilities
by contact network and the effects of NPIs, see Supplementary
Material~\ref{subsec:estimated_params}---will be chosen numerically so that the model
matches features of the data \citep[see][for the general method, also described in
Supplementary Material \ref{sec:model}]{McFadden1989}.\comment[id=HM]{Make reference more
specific once Appendix has new structure} In our application, we keep the number of free
parameters low in order to avoid overfitting. The data features to be matched include
official case numbers for each age group and region, deaths, and the share of the B.1.1.7
strain.

The main issue with official case numbers is that they will contain only a fraction of
all infections. We thus model official cases as depicted in
Figure~\ref{fig:model_official_cases}.\comment[id=K]{I don't understand why we mention
the false positive rates in the floatfoot of this. I would either mention rapid test
sensitivity and specificity in general or not mention them at all.} We take aggregate
estimates of the share of detected cases and use data on whether CoViD-19 symptoms led to
a PCR test. As the share of asymptomatic individuals varies by age group, this gives us
age-specific shares (see Figure~\ref{fig:share_known_cases_by_age_group} for the share of
known cases by age group over time in our model). Our estimates suggest that---in the
absence of rapid testing---the detection rate is on average 80\% higher for individuals
above age 80 compared to school age children. Once rapid test become available,
confirmation of a positive result is another reason leading to positive PCR tests.
